Supplementary Materials

### 2018-03-24 paper/appendix_modelDescription.tex
update appendix

\usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.

@@

%% Paper title.
\title{
NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models
%Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference Models
}
%% This is how authors are specified in the journal style

%% indicate IEEE Member or Student Member in form indicated below
% \author{Roy G. Biv, Ed Grimley, \textit{Member, IEEE}, and Martha Stewart}
% \authorfooter{
% %% insert punctuation at end of each item
% \item
%  Roy G. Biv is with Starbucks Research. E-mail: roy.g.biv@aol.com.
% \item
%  Ed Grimley is with Grimley Widgets, Inc.. E-mail: ed.grimley@aol.com.
% \item
%  Martha Stewart is with Martha Stewart Enterprises at Microsoft
%  Research. E-mail: martha.stewart@marthastewart.com.
% }

%other entries to be set up for journal
\shortauthortitle{Natural Language Inference Model Visualization}
%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances in deep learning, neural network based models have obtained state-of-the-art performances for many linguistic tasks in natural language processing. The disruptive progress also brings enormous challenges. The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms. In this work, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model allows a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline. We use natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states and interpreting and hypothesizing the fundamental model mechanism such as attention.
} % end of abstract

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
\keywords{Natural Language Processing, Interpretable Machine Learning, Natural Language Inference, Attention Visualization}

%% ACM Computing Classification System (CCS).
%% See <http://www.acm.org/class/1998/> for details.
%% The ``\CCScat'' command takes four arguments.

% \CCScatlist{ % not used in journal version
%  \CCScat{K.6.1}{Management of Computing and Information Systems}%
% {Project and People Management}{Life Cycle};
%  \CCScat{K.7.m}{The Computing Profession}{Miscellaneous}{Ethics}
% }

%% Uncomment below to include a teaser figure.
% \teaser{
%   \centering
%   \includegraphics[width=\linewidth]{CypressView}
%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
% 	\label{fig:teaser}
% }
\teaser{
% \vspace{-8mm}
 % \includegraphics[width=0.78\linewidth]{teaser}
 \includegraphics[width=.96\linewidth]{teaser.pdf}
 \centering
 % \vspace{-3mm}
  \caption{
 System overview.
  }
\label{fig:teaser}
}

%% Uncomment below to disable the manuscript note
%\renewcommand{\manuscriptnotetxt}{}

%% Copyright space is enabled by default as required by guidelines.
%% It is disabled by the 'review' option or via the following command:
% \nocopyrightspace

\vgtcinsertpkg

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%% The ``\maketitle'' command must be the first command after the
%% ``\begin{document}'' command. It prepares and prints the title block.

%% the only exception to this rule is the \firstsection command
\input{intro.tex}
\input{background.tex}
\input{relatedWorks.tex}

\input{task.tex}
\input{pipeline.tex}
\input{perturbation.tex} % how to do the perturbation
\input{sentence.tex}
\input{attention.tex} % how to encode the information
\input{prediction.tex}

\input{application.tex}

\input{evaluation.tex}
\input{discussion.tex} % how to encode the information

%% if specified like this the section will be committed in review mode
% \acknowledgments{
% The authors wish to thank A, B, and C. This work was supported in part by
% a grant from XYZ (\# 12345-67890).}

%\bibliographystyle{abbrv}
\bibliographystyle{abbrv-doi}
%\bibliographystyle{abbrv-doi-narrow}
%\bibliographystyle{abbrv-doi-hyperref}
%\bibliographystyle{abbrv-doi-hyperref-narrow}

\bibliography{entailVis.bib}
\end{document}

>>>>

\usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
\usepackage{listings}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    %breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

@@

%% Paper title.
\title{
Supplementary Materials
%Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference Models
}
\vgtcinsertpkg

\begin{document}
\firstsection{Appendix 1, Detailed description of the Model}
\maketitle

\section{Appendix 2, Code Example: Link Visualization with Model}
\begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
from visPackage import *
from modelInterface import *
from sentenceGenerator import *

#initialize NLP model
model = modelInterface(
    wordDict="../data/snli_1.0/snli_1.0.word.dict",
    wordVec="../data/glove.hdf5", 
    model="../data/local_300_parikh")

#sentence perturbation
gen = sentenceGenerator()
#dependency parsing
dep = dependencyTree()

#define visualization components
visLayout = {
    "column":[{"row":["Selector", 
                                "Sentence", 
                                "Pipeline"]},
            {"row":["AttentionGraph", 
                       "AttentionMatrix", 
                       "Prediction"]}]
    }

#create vis interface
vis = textEntailVisModule(visLayout)

#setup model callbacks
vis.setPredictionHook(model.predict)
vis.setAttentionHook(model.attention)
vis.setPredictionUpdateHook(model.updatePrediction)
vis.setAttentionUpdateHook(model.updateAttention)
vis.setReloadModelCallback(model.reloadModel)
vis.setPipelineStatisticHook(model.pipelineStatistic)

#setup perturbation and grammar parsing callbacks
vis.setSentencePerturbationHook(gen.perturbSentence)
vis.setSentenceParserHook(dep.getDependencyTree)

#open browser to show visualization
modelVis.show()

\end{lstlisting}

\end{document}

### 2018-03-24 paper/relatedWorks.tex
update appendix

\noindent\textbf{Visual Exploration of Neural Networks.}
The effectiveness in the exploration of complex relationships, visualization have long been adopted for interpreting neural network models (e.g., the early works such as~\cite{TzengMa2005})
Recently, many visualization works has dedicated to the neural network model interpretability challenges.
% The classification~\cite{KrausePererNg2016}
In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzing classification errors in convolutional neural networks and answer the question on whether class hierarchy is learn in the network.
Liu et al.~\cite{LiuShiCao2018} explore the possiblility of understanding the training process of deep generative models.
The ActiVis~\cite{KahngAndrewsKalro2018} focus on large scale network in real world setting.
The DeepEyes~\cite{Pezzotti2018} focuses on the analyzing the training procss, so they can provide design guideline to the deep neutral network architect.

@@

\noindent\textbf{Neural Linguistic Model Visualization.}
Compare to the multitude of researchs for making sense of convolutional neural networks, relatively less works has been dedicated to neural linguistic models.
%
However, the previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models, but also revealed enoumous possibility for future applications.
% There is many unresolve challenge and the
The early work on charactor level recurrent network~\cite{KarpathyJohnson2015} demonstrates effectness of the hidden state in capturing the unique pattern in training text. The compositionality exibited in neural linguistic model (i.e., build sentence from meaing of words and phrases) are examined in the work by Li et al. ~\cite{LiChenHovy2015}, by utilizing methods inspired by similar work in computer vision.
The LSTMvis~\cite{StrobeltGehrmannPfister2018} work utilized a line plot style visual encoding to visualize the time varying hidden states of recurent neutural network. The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrate how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space produced by word2vec~\cite{MikolovSutskeverChen2013} or glove~\cite{PenningtonSocherManning2014}.

>>>>

\noindent\textbf{Visual Exploration of Neural Network Models.}
Due to the effectiveness for exploring complex relationships, visualization have long been adopted for interpreting neural network models~\cite{TzengMa2005}.
Recently, the increasingly apparent interpretability challenge for deep neural network model motivate the introduction of many visualization works has dedicated to the neural network models.
% The classification~\cite{KrausePererNg2016}
In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzing classification errors in convolutional neural networks and answer the question on whether class hierarchy is learn in the network.
Liu et al.~\cite{LiuShiCao2018} explore the possibility of understanding the training process of deep generative models.
The ActiVis~\cite{KahngAndrewsKalro2018} focus on large scale network in real world setting.
The DeepEyes~\cite{Pezzotti2018} focuses on the analyzing the training process, so they can provide design guideline to the deep neutral network architect.

@@

\noindent\textbf{NLP Models Visualization.}
Compare to the multitude of research for making sense of convolutional neural networks, relatively less works has been dedicated to neural linguistic models.
%
However, the previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models, but also revealed enoumous possibility for future applications.
% There is many unresolve challenge and the
The early work on charactor level recurrent network~\cite{KarpathyJohnson2015} demonstrates effectness of the hidden state in capturing the unique pattern in training text. The compositionality exibited in neural linguistic model (i.e., build sentence from meaing of words and phrases) are examined in the work by Li et al. ~\cite{LiChenHovy2015}, by utilizing methods inspired by similar work in computer vision.
The LSTMvis~\cite{StrobeltGehrmannPfister2018} work utilized a line plot style visual encoding to visualize the time varying hidden states of recurent neutural network. The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrate how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space produced by word2vec~\cite{MikolovSutskeverChen2013} or glove~\cite{PenningtonSocherManning2014}.
